Presented is a search in the high mass dielectron spectrum for beyond the Standard Model physics exhibiting a non resonant behaviour. New physics processes such as four fermion contact interactions and the ADD model with large extra dimensions, are searched for with the ATLAS detector using proton-proton collisions from the Large Hadron Collider at CERN. Results from two data sets are presented, the main results presented come from a data set with $\sqrt{s}$ = 8~TeV and an integrated luminosity of 20.3~fb$^{-1}$, these results are compared to a data set with $\sqrt{s}$ = 7~TeV and an integrated luminosity of 4.9~fb$^{-1}$ completed prior. The main analysis was a search in the dielectron invariant mass distribution as well as the angular variable $\cos{\theta^{*}}$, while the 7 TeV analysis searched in the dielectron invariant mass. 

No significant signal is found in either data set and so lower limits are set on the scale of new physics for several formalisms of each model. 
For the 7~TeV analysis limits on the scale of new contact interactions ($\Lambda$) are set for the bench mark formalism of LL contact interactions of $\Lambda$ $>$ 12.7~TeV and $\Lambda$ $>$ 9.63~TeV for the model for constructive and destructive interference with the Drell-Yan background respectively. In the same analysis limits are set on the ADD model scale of new physics (M$_{S}$) of M$_{S}$ $>$ 3.0~TeV on the benchmark formalism GRW.

The 8 TeV analysis sets higher limits on the LL formalism of $\Lambda$ $>$ 21.55 TeV and $\Lambda$ $>$ 19.61 TeV for constructive and destructive interference. Limits are also set on other formalisms with the highest limits set on the LR formalism of $\Lambda$ $>$ 26.25 TeV and $\Lambda$ $>$ 23.77 TeV for constructive and destructive interference. Limits are set on the ADD GRW formalism of M$_{s}$ $>$ 4.79 TeV with limits on other formalisms also presented. At the time of writing these are the highest public limits set on either theoretical models.



